\section{Background}

%Describe the greater context, what are the technologies and protocols figuring in this thesis.
%In beginning mention a little bit of both IoT and ICN sort of waving them together.
%
%\begin{itemize}
%\item Describe the greater contest, what are the technologies and protocols figuring in the thesis.
%\item Mention both IoT and ICN and wave them together somehow.
%\item describe the growing number of IoT devices.
%\end{itemize}
By 2020 a total of 50 billion IoT units is estimated to be installed world wide. It represents a staggering 30 time increase from the year of 2009, where a total of 0.9 billion units was installed \cite{alanCarlton}\cite{Gartner}.  The increase in demand for IoT-related equipment and services has led to several major manufacturers joining the market, which in turn led to several different communcation standards which the IoT devices communicates with being developed. 
\todo{Big jump in context here from IoT overall to communication. Try to bridge that with one more sentense. /b}

A new communication protocol is not developed overnight. It takes a lot amount of research and time to develop a new protocol. A majority of the network protocols and systems in this thesis were developed during the 1990s or early 2000. Although the term ICN was coined in 2000 with the TRIAD paper \cite{TRIAD}, it was not until Jacobsson et al in 2009 \cite{Jacobson2009}, it started to draw wider attention.

Each operating system and protocol of communication has its own restrictions and possibilities in delivering sensor data from a producer to a consumer.
In this section, the systems and protocols used in this thesis are described which can be applied in wireless sensor networks.
\todo{Would be good with slighyly more detail on what comes next. (not top prio.)/ B}

\input{section/background/iot.tex}

\input{section/background/ccn.tex}

\input{section/background/contiki.tex}

%\input{section/background/hardware.tex}
