\section{Implementation}

In order to evaluate the two major fields stated in the problemstatement, there are two thigns that has to happen.


\begin{itemize}
\item Utveckla problem statement

\item This is the problem
\item Continue more in depth than problem statement in chap 1.
\item That leds us to these experiments and why theyre done.
\end{itemize}
fakpweofkpwaef
\begin{itemize}
\item These are the problems that we want to solve.
\item Thats why we have developed these experiments.
\item For one, the latency difference between ping and peek evaluation.
\item Second, A evaluation regarding the algortim that makes it possible to `Deliver the data with as low latency possible from the sensor to the applicant.'


\end{itemize}

The thesis is therefore devided into two major experiments. First, in section [performance], latency performance experiments between ping and CCN peek are evaluated. [Continue write about why we need the performance evaluation.]
Secondly, experiments around the feasibility evaluation
Secondly, an evaluation regarding the feasibility experiments is made in section [feasibility]. 

Thatis why we have developed two major experiments, first concentrating on the latency performance evaluation between ping and CCN peek. The second experiment is made to evaluate `how deliver low latency '

ICN is by nature a pull paradigm where a consumer has to initiate a request of a particular data object in order to retrive it. This is in constrast to several IoT systems where the publish/subscribe approach is more common. An example of such a system is MQTT [3] where the producer sends the newly created data towards a broker, which then pushes the data to a user/consumer. By evaluating the feasibility, a major goal is to investigate if it is possible to achive similar outcome with ICN together with a onetime subscription model and if such a system would be stable. With the onetime subscription model, a consumer tries to pull the data from the producers by initiating a request just before the data has been created.


The theses tries to answer the question if ICN/CCN together with a one time subscription approach, could lead to that the latency in time from when the data is created is minimized, or as small as possible, equivivalent to MQTT. 

In the problem statement, 

The question the thesis tries to answer is wheather or not the client-server model, as in MQTT or similar, could be replaced with the information-centric model, and CCN, instead. The problem with the ICN model in IoT domain, lays in the nature of ICN with its data driven communication paradigm. A data will only pass through the network if it has been requested. In a normal network approach, a creator of a data can push its data toward a user. This is impossible with the ICN paradigm. 

The problem remains from a user/consumer perspecitve. It wants the data from the sensors as soon as it has been created, it does not matter wheater how it is done, but that it is done. 

In order to retrieve the data as soon as possible, a couple of experiments has to be evaluated in order to see if CCN could fit. That's why we have done two major experiments. one conserning the latency approach with CCN, A comparision between the CCN and ping is evaluated to see if ccn have large compuattion times that could harm the time it takes to process a request. 
secondly, experiments regardign how to retrieve data as soon as it has been produced in a periodically manner is discovered.



In order to invesigate wheather or not it is possible, the




\subsection{Setup}

Some info about why this is the setup. Maybe because of the previous section.
\begin{itemize}
%\item Hardware, copy from current background.
%\item Software, CCN application for SN and GW and write about ping6.
%\item Communication flow between gateway and sensor. EVERYthing thats happening then, from application layer from gw to sn.
%\item Debugging/printing to collect information.
\item Ingress.
\item Create a picutre that connects the dots, refere to this picture in the subsections.
%\item delim in setup (mayBE)
\end{itemize}


\input{section/implementation/hardware.tex}

\input{section/implementation/software.tex}

\input{section/implementation/communication.tex}

\input{section/implementation/debug.tex}